Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-24 paper/paper.tex
Update SPSS planning time figure/text

\subsection{Failures}
\label{sec:failures}

@@

Figure~\ref{fig:spss_planning_time} shows the SPSS planning time for three different ensemble sizes (50, 100, 200), and five different workflow sizes (50, 200, 400, 600, 800). The ensembles were generated using a constant distribution equal to the workflow size desired. Two different applications were used: SIPHT and CyberShake. Each box summarizes the results of 2 applications, 10 random seeds, 10 budgets and 10 deadlines, or 2000 simulations per box. For ensemble size 200, the results for workflow size 800 are omitted because the simulations took too long to get a representative sample.

Figure~\ref{fig:spss_planning_time} shows that, for small ensembles and small workflows, the SPSS planning time is reasonable, taking on the order of tens of seconds to a few minutes. For larger ensembles of large workflows, however, the SPSS planning time can easily reach 10-15 minutes. Considering that the largest workflows used in this experiment are rather small (maximum of 800 tasks), and that real workflows are often much larger (workflows with tens of thousands of tasks are common, and workflows with hundreds of thousands or millions of tasks are rare but do exist), it is unlikely that SPSS will be practical for ensembles of very large workflows.

\begin{figure*}[t]
    \includegraphics[width=\textwidth]{spss_planning_time}
    \caption{Planning time of SPSS algorithm for different ensemble and workflow sizes.}
    \label{fig:spss_planning_time}
\end{figure*}

>>>>

\subsection{Task Failures}
\label{sec:failures}

@@

Figure~\ref{fig:spss_planning_time} shows the SPSS planning time for ensembles of 100 workflows with five different workflow sizes: 50, 200, 400, 600, and 800 tasks. The ensembles were generated using a constant distribution equal to the workflow size desired. Two different applications were used: SIPHT and CyberShake. Each box summarizes the results of 2 applications, 10 random seeds, 10 budgets and 10 deadlines, or 2000 simulations per box.

Figure~\ref{fig:spss_planning_time} shows that, for small workflows, the SPSS planning time is reasonable, taking on the order of tens of seconds to a few minutes. For larger ensembles of large workflows, however, the SPSS planning time can easily reach 10 minutes. Considering that the largest workflows used in this experiment are still relatively small (maximum of 800 tasks), and that real workflows are often much larger (workflows with tens of thousands of tasks are common, and workflows with hundreds of thousands or millions of tasks are not impossible), it is unlikely that SPSS will be practical for ensembles of very large workflows.

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.4\textwidth]{spss_planning_time}
    \caption{Planning time of SPSS algorithm for ensembles of 100 workflows and different workflow sizes.}
    \label{fig:spss_planning_time}
\end{figure}
